Gravitational field calculation in spherical coordinates using variable densities in depth

### 2019-06-06 manuscript/manuscript.tex
Add the SOEST number and thank the editor/reviewers (#62)
Fixes #60

We have implemented the algorithms described in the previous sections in the Python
programming language.
The software is based on the Python implementation of \citet{Uieda2016} that is included
in the Fatiando a Terra library v0.5 \citep{Uieda2013}.
The more time consuming parts of the algorithm are written in the Cython language to
achieve higher performance.
We leverage the dynamic nature of the Python language to allow user-defined radial
density functions as inputs to the software.
Thus, our code can evaluate linear, exponential, polynomial, sinusoidal, cubic splines,
or any other continuous density function without modification.
This new code is freely available under the BSD 3-clause open-source license.
It can be freely downloaded from the online repository
\href{https://github.com/pinga-lab/tesseroid-variable-density}{github.com/pinga-lab/tesseroid-variable-density}.

@@

We are indebted to the developers and maintainers of the open-source software without
which this work would not have been possible.

>>>>

We have implemented the algorithms described in the previous sections in the Python
programming language.
The software is based on the Python implementation of \citet{Uieda2016} that is included
in the Fatiando a Terra library v0.5 \citep{Uieda2013}.
The more time consuming parts of the algorithm are written in the Cython language to
achieve higher performance.
We leverage the dynamic nature of the Python language to allow user-defined radial
density functions as inputs to the software.
Thus, our code can evaluate linear, exponential, polynomial, sinusoidal, cubic splines,
or any other continuous density function without modification.
This new code is freely available under the BSD 3-clause open-source license.
All source code, Python scripts, data, and model results are made available through
an online repository
\href{https://doi.org/10.6084/m9.figshare.8239622}{doi.org/10.6084/m9.figshare.8239622}
\citep{Soler2019} or
\href{https://github.com/pinga-lab/tesseroid-variable-density}{github.com/pinga-lab/tesseroid-variable-density}.
The repository also contains instructions for replicating all results
presented here.

@@

We are indebted to the developers and maintainers of the open-source software without
which this work would not have been possible.
We would also like to thank editor Kosuke Heki and two anonymous reviewers for their
comments and contributions.
This is SOEST contribution 10717.
